### 2016-03-22 Paper_v5.tex
Added discussion on sub-swarm influence

\subsection*{Influence of the number of sub-swarms on DOPS performance.}

@@

>>>>

\subsection*{Influence of the number of sub-swarms on DOPS performance.}
We attempted to quantify the influence of sub-swarms and DDS phase on the error convergence rates. To do so we considered only the multi swarm search without the DDS phase for 4000 function evaluations and 40 particles on the coagulation model. While doing the multi swarm search without DDS we varied the number of sub-swarms as one, two, four, five and eight. The number of sub-swarms were chosen so that each swarm contained the same number of particles. Hence we did not consider swarm numbers of three and seven. All the other parameters remained the same for each of these searches. We observed that the higher sub-swarm numbers had faster convergence rates with eight having the fastest rate. However this difference in convergences is not pronounced amongst four, five and eight. This suggests that there is an optimal number of particles per swarm beyond which there is no significant advantage.

We also observe that when these convergence rates are compared with DOPS, DOPS shows a very rapid drop when the swarm searches begin to saturate. The green region indicates when swarm search switches to a DDS based search. As we see in (Fig. ) the error convergence rates tend to remain mostly flat for the purely swarm searches with different swarm numbers. However in DOPS as soon as convergence rate begins to saturate it automatically switches to a DDS phase which leads to a more pronounced drop. Thus this automated switching strategy appears to be crucial in leading the algorithm out of local optima or saddle point regions.

@@

\begin{table}[h]
\centering
\caption{Error Analysis.}
\label{table:Error-Analysis}
\begin{center}
\begin{tabular}{ |c|c|c|c| } 
\hline
Simulation&Concentration& Normalized Standard Error  \\
\hline
\multirow{3}{4em}{FVIIa-TF level} & 5nM & 0.0376\\ 
& 500pM & 0.0564\\
& 50pM & 0.1125\ 
& 10pM & 0.0823 \\
& 5pM & 0.0338 \\ 
\hline
\end{tabular}
\end{center}
\end{table}
